Generative AI for image reconstruction in Intensity Interferometry: a first attempt

### 2025-10-06 Phase_II/draft/ParaGanX.tex
changing some file names

The process to train the model is summarized here:
\iffalse
\begin{figure*}[htbp]
	%\centering
	\begin{center}
		\begin{tikzpicture}[node distance=0.7cm]

@@

		\end{tikzpicture}
	\end{center}
\caption{A block diagram for the process of image reconstruction through GAN.}
\end{figure*}
\fi

\iffalse
\documentclass{article}
\usepackage{tikz}
\usetikzlibrary{arrows, arrows.meta, positioning}

\tikzset{
  block/.style = {draw, rectangle, minimum height=1.5em, minimum width=3em, align=center},
  arrow/.style = {->, thick},
}

%\begin{document}
\fi

\begin{figure}[htbp]
\centering
\begin{tikzpicture}[node distance=0.9cm]
%\begin{tikzpicure}[scale = 0.5]

% Training, Validation, Testing
\node[block, fill=green!15, below left=0.6cm and 2.5cm of split] (train) {Training Set \\ (Learn Model Parameters)};
\node[block, fill=green!10, below=of split] (val) {Validation Set \\ (Tune Hyperparameters)};
\node[block, fill=green!05, below right=0.6cm and 2.5cm of split] (test) {Testing Set \\ (Final Evaluation)};

% Model training block
\node[block, fill=orange!20, below=3cm of val, minimum width=10cm, minimum height=1.2cm] (mod) {Train the Model \\ (Generator + Discriminator)};

% Generator side (left)
\node[block, fill=yellow!15, below=1.2cm of mod, xshift=-3.5cm] (noise) {Random Noise $z$};
\node[block, fill=blue!10, below=of noise] (gen) {Generated Image $\hat{x}$};
\node[block, fill=purple!20, below=of gen] (gloss) {Generator Loss \\ (Update $G$)};

% Discriminator side (right)
\node[block, fill=yellow!20, below=1.2cm of mod, xshift=+3.5cm] (real) {Real Image \\ (From Training Set)};
\node[block, fill=orange!20, below=of real] (disc) {Discriminator $D(x)$};
\node[block, fill=red!20, below=of disc] (out) {Discriminator Output};
\node[block, fill=purple!30, below=of out] (dloss) {Discriminator Loss \\ (Update $D$)};

% Final result block
\node[block, fill=teal!20, below=4.2cm of val, minimum width=5cm] (res) {Result / Evaluation \\ (Performance Metrics: Accuracy)};

% Connections
\draw[arrow] (data) -- (pre);
\draw[arrow] (pre) -- (split);
\draw[arrow] (split.south west) |- (train.north);
\draw[arrow] (split.south) -- (val.north);
\draw[arrow] (split.south east) |- (test.north);
\draw[arrow] (train.south) -- (mod.north);

% Validation & Testing to Result
\draw[arrow] (val.south) -- (res.north);
\draw[arrow] (test.south) -- (res.north);

\end{tikzpicture}
\end{figure}

%\end{document}

>>>>

The process to train the model is summarized here:
\begin{figure*}[htbp]
	%\centering
	\begin{center}
		\begin{tikzpicture}[node distance=0.7cm]

@@

		\end{tikzpicture}
	\end{center}
\caption{A block diagram for the process of image reconstruction through GAN.}
\end{figure*}
